Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-05-04 paper.tex
Reviewing Introduction pt. II

It is important to notice that the accuracy of the predictive method that we intend to design is affected negatively by several factors, related to decisions on purchases, to freight traffic, or with the distribution strategy \cite{Little1998}.
Thus, it is mandatory to know the product and the variables that
might affect the sales, and how an expert manager takes them into 
account \cite{Armstrong2001,SThomassey2014}. 
Moreover, their impact is difficult to estimate and it is not constant over time, hence the difficulty to adequately identify and measure their influence \cite{DeToni2000}.
In addition, some may have correlations between them. 
However, these correlations can be detected using data analysis methods, 
such as Self-Organizing Maps (SOM) \cite{kohonen1998} or stepwise regression analysis (SRA) \cite{Chang2009}.

So, we will analyze in this work the data by means of different data mining methods and create predictive models that can be used mainly as decision-aid tools for book publishers. Then, they will be able to combine their expert-knowledge about the market with the created forecasting models in order to get a reliable estimation of book sales.

% Antonio - I think this is the main idea we have to sell in this paper. Due to the  difficulty of the book sales market (and its variables), we cannot give an accurate tool for predicting book sales, but a decision-aid tool for publishers. Do you agree?

>>>>

It is important to notice that the accuracy of the predictive method that we intend to design is affected negatively by several factors related to decisions on purchases, to freight traffic, or with the distribution strategy \cite{Little1998}.
Thus, it is mandatory to know the product and the variables that
might affect the sales, and how an expert manager takes them into 
account \cite{Armstrong2001,SThomassey2014}. 
Moreover, their impact is difficult to estimate and it is not constant over time, hence the complexity to adequately identify and measure their influence \cite{DeToni2000}.
In addition, some may have correlations between them, although these correlations can be detected using data analysis methods, 
such as Self-Organizing Maps (SOM) \cite{kohonen1998} or stepwise regression analysis (SRA) \cite{Chang2009}.

Therefore, in this work we analyse the data by means of different data mining methods and create predictive models that can be mainly used as decision-aid tools for book publishers. Then, they will be able to combine their expert knowledge about the market with the created forecasting models in order to get a reliable estimation of book sales.

% Antonio - I think this is the main idea we have to sell in this paper. Due to the  difficulty of the book sales market (and its variables), we cannot give an accurate tool for predicting book sales, but a decision-aid tool for publishers. Do you agree?
% (Paloma) Agree
